Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-29 lloveras_2020.tex

\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}

@@

{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops. To this end, we applied the technique developed by \citet{maccormack_2017}. We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$. A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves.}

>>>>

%\keywords{Solar Cycle, Observations; Corona,E; Corona, Structures}
\keywords{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}

@@

{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops. To this end, we applied the technique developed by \citet{maccormack_2017}. We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$. A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}
